A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading

### 2020-06-18 paper.tex
Add blind signature description

\begin{abstract} 
%cite IoT data subscription economy
The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us. Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources. The real-time data exchangements among devices forms a publish/subscribe (pub/sub) relationship of streaming data which devices can transform the data exchangement into subscription-based services. However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification. Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threaten the trust foundation of the entire system. Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants. Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automatic subscription procedures is also required. In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data trading platform on top of the IoT brokered infrastructure. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts. Finally, the prototype is implemented and evaluated.
\end{abstract}

@@

\section{Introduction}
In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS}, and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories ,and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers and data consumers meet.

Among the challenges of data trading platform\cite{BigDataMarket}, we conclude the following four essential requirements:
\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
\end{itemize}

%publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we aim for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements. As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline. For example, the Internet of Vehicles (IoV) allows vehicles to connect with traffic signs and bicycles, share information, and at the same time be able to understand the real-time environmental conditions and find the best route through the communication. While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV. Therefore, the publish/subscribe (pub/sub) communication model that provides the flexibility of following and unfollowing the data streams for users is more appropriate in the IoT scenarios.

@@

%trustless & automated
%trust: 對系統、對身份、對資料
In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading. Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform. In current systems, trusted third-party authority like CA is widely adopted to certify each member. However, building trust upon CA is dangerous and fragile. The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion. Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}. Besides CA and storage, the subscrition history of data consumer reveals his/hers interests and the exposure of personal information during trading process against GDPR as well. The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.

Thus, the data trading platform for IoT towards a decentralized and trustless design. In this paper, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure. See Fig.~\ref{fig:system_design}. The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically. The trading processes are automated with smart contracts, which allows devices focus on their jobs while gaining the rewards. Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.

@@

\section{System Design Thinking}
\subsection{The Architecture}
% TODO: pub/sub model selection
There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. As shown in Fig.~\ref{fig:system_design}.

@@

@@

\subsection{Enable Automated Trading Process}
% Ethereum Smart Contract
% use ethereum smart contract => IOTA smart contracts are still under development
Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. 
It provides the smart contract, which is a protocol for formulating agreement on a blockchain that running on decentralized virtual machines. A smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency. All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it will be executed automatically without any third-parties and it is uninterruptible.

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be acheived. \textbf{Product Contract} is made for the product launching and trading process in the decentralized data marketplace. The information of data products such as MAM channel ID (the data entry point), data price, time period and the broker-verified encryption key are listed on Product Contract. Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of both providers and subscribers.

>>>>

\begin{abstract} 
%cite IoT data subscription economy
The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us. Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources. The real-time data exchangements among devices forms a publish/subscribe (pub/sub) relationship of streaming data which devices can transform the data exchangement into subscription-based services. However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification. Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threaten the trust foundation of the entire system. Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants. Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automatic subscription procedures is also required. In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct a decentralized and trusted data trading platform on top of the IoT brokered infrastructure. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts. Finally, the prototype is implemented and evaluated.
\end{abstract}

@@

\section{Introduction}
In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS}, and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing mechanism where data providers and data consumers meet.

%publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we aim for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData}. As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline. For example, the Internet of Vehicles (IoV) allows vehicles to connect with traffic signs and bicycles, share information, and at the same time be able to understand the real-time environmental conditions and find the best route through the communication. While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV. Therefore, the publish/subscribe (pub/sub) communication model that provides the flexibility of following and unfollowing the data streams for users is more appropriate in the IoT scenarios.

@@

%trustless & automated
%trust: 對系統、對身份、對資料
In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading. Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform. In current systems, trusted third-party authority like CA is widely adopted to certify each member. However, building trust upon CA is dangerous and fragile. The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion. Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}. Besides CA and storage, the subscrition history of data consumer may reveal his/hers interests and the exposure of personal information during trading process against GDPR as well. The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.

Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following four essential ones:
\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
\end{itemize}

Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design. In this paper, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure. See Fig.~\ref{fig:system_design}. The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically. The trading processes are automated with smart contracts, which allows devices focus on their jobs while gaining the rewards. Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.

@@

\section{System Design Thinking}
\subsection{Data trading platform players}
There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. As shown in Fig.~\ref{fig:system_design}.

@@

We adopt the brokered infrastructure for three reasons. Firstly, it inherits the benefits from the standard pub/sub model which is more efficient than the request/response model specifically in a large scale system. Furthermore, if either side is offline, the proceeding tasks have to stop and start over. With brokers, the unfinished work can be cached or accomplished. Second, a fully decentralized architecture has difficulties to brings data providers and consumers together, both of them need to reveal more sensitive information, such as IP address, in order to build the communication tunnel. The existence of brokers resolved the privacy issue, as brokers are the bridges that link data providers and consumers, participants can trade with minimum info like its identifier and public key. Third, as brokers running on machines in a stable network and electricity environment, besides matching procedures, participants on resource-constrained devices can offload the computation tasks to brokers. In our proposed protocol, devices can delegate the uploading and trading processes to brokers after signing the data, and brokers can perform verifiable checks without knowing the contents.

@@

\subsection{Enable Automated Trading Process}
Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. It provides the smart contract, which is a protocol for formulating agreement on a blockchain that running on decentralized virtual machines. A smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency. All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be acheived. In our system, \textbf{Product Contract} is made for the product launching and trading. The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract. See Listing. \ref{lst:constructor}. Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants.

The transparency of smart contracts bring advantages for data providers and consumers. One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively. For data providers, with every details opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/her has. The consumer list and the states of products, which includes \textit{Launched, KeyCertified, Finished} and \textit{Refunded} are key reputation referenced for data consumers to decide whether to subscribe.

\lstdefinestyle{solidity}{
	captionpos=b,
	tabsize=4,
	basicstyle=\scriptsize
}
\lstset{style=solidity}
\begin{lstlisting}[caption={Product Contract data fields}, label={lst:constructor}, frame=single]
contract Product {
    address public broker;
    address public provider;
    bool isBrokerWithdraw;
    bool isProviderWithdraw;
    address[] consumers;

    struct Purchase {
        bool affirmativeVote;
        bool isConsumerWithdraw;
        bool isKeyAdded;
        string encryptKey;
    }
    mapping(address => Purchase) public consumer2Purchase;

    uint public price;
    uint public totalAmount;
    uint public brokerage;
    uint public threshold;
    string public channelRoot;
    string public endPoint;
    uint public totalNumber;
    uint public uploadedNumber;
    uint public affirmativeVotes;
    string blindedKey;
    string signedBlindedKey;

    enum State {Launched, KeyCertified, Finished, Refunded}
    State public state;
}
\end{lstlisting}

\subsection{Enable delegation of computation tasks to broker}
To participate data subscription, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks. However, the resources of low-level devices are precious which should be used to focus on its jobs. Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.

The delegation should also ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts. To deal this issue, we use blind signature\cite{blindSig} to allow brokers to certify and update the sensitive contents without knowing it. Blind signature is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign. Figure \ref{fig:blind_signature} illustrates the steps of blind signature. The resulting message, along with the blinding factor, can be later verified with the signer's public key. 
% TODO: redraw blind signature diagram
% TODO: broker 進行簽章的必要性

RSA blind signature\cite{cryptoNote} is used in our research. The user chooses a random number $r$ and uses the signer's public key $e$ to generate a blinding factor $r^e$. To prevent the message $m$ from being known by the signer, the user sends blinding message $c$ to the signer instead of $m$.

\begin{equation}
C = r^e m
\end{equation}

The signer signs the blinding message with his private key $d$.

\begin{equation}
S = C^d
\end{equation}

$S$ is the signer's signature of $C$. In RSA system, $ed$ is equal to 1. To remove the blinding factor, the user computes the following calculation.

\begin{equation}
\frac{S}{r}= \frac{C^d}{r} = \frac{(r^e m)^d}{r} = \frac{r^{ed} m^d}{r} = m^d
\end{equation}

The user gets $m^d$ which is the signer's signature of the message $m$. At the same time, the signer does not know $m$ and the session key is protected.

\subsection{Enable delegation of computation tasks to broker}
To participate data subscription, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks. However, the resources of low-level devices precious which should be used to focus on its jobs. Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.

The delegation should also ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts. To deal this issue, we use blind signature\cite{blindSig} to allow brokers to certify and update the sensitive contents without knowing it. Blind signature is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign. Figure \ref{fig:blind_signature} illustrates the steps of blind signature. The resulting message, along with the blinding factor, can be later verified with the signer's public key. 
% TODO: redraw blind signature diagram
% TODO: broker 進行簽章的必要性

RSA blind signature\cite{cryptoNote} is used in our research. The user chooses a random number $r$ and uses the signer's public key $e$ to generate a blinding factor $r^e$. To prevent the message $m$ from being known by the signer, the user sends blinding message $c$ to the signer instead of $m$.

\begin{equation}
C = r^e m
\end{equation}

The signer signs the blinding message with his private key $d$.

\begin{equation}
S = C^d
\end{equation}

$S$ is the signer's signature of $C$. In RSA system, $ed$ is equal to 1. To remove the blinding factor, the user computes the following calculation.

\begin{equation}
\frac{S}{r}= \frac{C^d}{r} = \frac{(r^e m)^d}{r} = \frac{r^{ed} m^d}{r} = m^d
\end{equation}

The user gets $m^d$ which is the signer's signature of the message $m$. At the same time, the signer does not know $m$ and the session key is protected.
